The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-13 outputs/docs/events/paper.Rmd
removed the heres so monica could compile

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
```

@@

```{r mu1to20, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/mu_topic1-20.pdf"))
```

```{r mu21to40, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/mu_topic21-40.pdf"))
```

```{r mu41to60, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/mu_topic41-60.pdf"))
```

@@

```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/example_hansard_page.png"))
```

>>>>

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example.pdf")
```

@@

```{r mu1to20, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/mu_topic1-20.pdf")
```

```{r mu21to40, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/mu_topic21-40.pdf")
```

```{r mu41to60, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/mu_topic41-60.pdf")
```

@@

```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
knitr::include_graphics("../../figures/example_hansard_page.png")
```
